\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-06-19 eg6-letters/NIM/EG6_RTPC_NIM.tex
Add gem production company

The new CLAS RTPC is a 250~mm long cylinder of 158~mm diameter, leaving just enough 
room to fit pre-amplifiers between the RTPC outer shell and the solenoid. The 
electric field is directed perpendicularly to the beam direction, 
such that drifting electrons are pushed away from the beam line. These electrons 
are amplified by three layers of curved GEMs and detected by the readout system 
on the external shell of the detector as illustrated in the 
Fig.~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves with 
independent GEM amplification systems that cover about 80\% of the azimuthal 
angle.

@@

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption{Image of a typical GEM foil similar to the one used for our RTPC 
\cite{GEM_ref_pic}.}

   \label{fig:GEMs}
\end{figure}

>>>>

The new CLAS RTPC is a 250~mm long cylinder of 158~mm diameter, leaving just enough 
room to fit pre-amplifiers between the RTPC outer shell and the solenoid. The 
electric field is directed perpendicularly to the beam direction, 
such that drifting electrons are pushed away from the beam line. These electrons 
are amplified by three layers of curved gas electron multipliers (GEM) and 
detected by the readout system 
on the external shell of the detector as illustrated in the 
Fig.~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves with 
independent GEM amplification systems\footnote{The foils were produced by 
Tech-Etch, Inc.} that cover about 80\% of the azimuthal 
angle.

@@

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption{Image of a typical GEM foil similar to the one used for our RTPC 
\cite{GEM_ref_pic}.} 
   \label{fig:GEMs}
\end{figure}
